---
title: "Basic Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wikimorphemesedit)
library(dplyr)
```

This package supplies tools to streamline the submission of multiple edits to
Wiktionary. The process currently still involves a bit of setup. This is partly
by design--we don't want to make it *too* easy to submit edits without having
more robust safeguards in place against undesirable edits.

This vignette assumes that we already have a list of edits we want to submit to
Wiktionary. For example:

```{r}
# see the vignette in {wikimorphemes} for suggestions on identifying edits
gs_url <- "https://docs.google.com/spreadsheets/d/11feSn_TzkfSHE2rG1VaBut8UG-yzezXqAgTcCQtAI0g/"

checked_candidates <- googlesheets4::read_sheet(ss = gs_url,
                                                sheet = "candidates") %>% 
  dplyr::filter(`correct?` == "y") %>%
  dplyr::select(word, possible_breakdown)

# before submitting edits, all proposed changes should be checked and rechecked
# by a competent human. We want to be good citizens of the wikiverse. :)
```

The general process is straightforward: loop through the edits, and submit them
one at a time.

```{r}

# first do a "dry run":

for (w in checked_candidates$word) {
  breakdown <- checked_candidates %>% 
    dplyr::filter(word == w) %>% 
    dplyr::pull(possible_breakdown)
  # there *should* be only one breakdown per word, but this is subject to 
  # human error, so let's check
  if (length(breakdown) > 1) {
    stop(paste("multiple breakdowns found for word:", w))
  }
  
  # the breakdown has been recorded as "baseword ## suffix". Extract pieces...
  pieces <- trimws(stringr::str_split(breakdown, "##", )[[1]])
  # in this particular case, we always have baseword + suffix
  base_word <- pieces[[1]]
  suffix <- pieces[[2]]
  # generate the edit that will be submitted to wiktionary. Be sure to use
  # the correct template here!!
  template <- generate_morphology_suffix_template(base_word = base_word, 
                                                  suffix = suffix)
  cat(w, ":", template, "\n")
}

# if the output from the above looks correct, we can change the loop to submit 
# the edits for real. We'll need to have our username and password in our 
# session environment
for (w in checked_candidates$word) {
  breakdown <- checked_candidates %>% 
    dplyr::filter(word == w) %>% 
    dplyr::pull(possible_breakdown)
  cat("doing word:", w, "\n")
  # the breakdown has been recorded as "baseword ## suffix". Extract pieces...
  pieces <- trimws(stringr::str_split(breakdown, "##", )[[1]])
  # in this particular case, we always have baseword + suffix
  base_word <- pieces[[1]]
  suffix <- pieces[[2]]
  # generate the edit that will be submitted to wiktionary. Be sure to use
  # the correct template here!!
  template <- generate_morphology_suffix_template(base_word = base_word, 
                                                  suffix = suffix)
  cat("submitting edit:", template, "\n")

  result <- submit_morphology_edit(word = w,
                                   template_text = template,
                                   my_username, my_password)
  cat("edit successful:", result, "\n") #TRUE if success
  Sys.sleep(5) # probably don't need to wait this long, but let's take it slow.
}

# Note that the edit will be aborted if no "Etymology" section exists yet.
# For now, those would have to be manually created.

```

The above code is a simple example. A more sophisticated loop would save the
results from each edit so that any unsuccessful cases could be examined.
